Species turnover reveals hidden effects of decreasing Nitrogen deposition in mountain hay meadows

### 2018-10-26 Manuscript.Rmd
Small edits in Data accessibiility.
Small additional edits in data accessibility chapter.

## Data accessibility and reproducibility of results {-}
Data and R Markdown documents (Manuscript.Rmd and Appendix_A.Rmd) to fully reproduce this manuscript including figures and tables are provided at https://github.com/TobiasRoth/NDep-Trend. An R Markdown document is written in markdown (plain text format) and contains chunks of embedded R code to produce the figures and tables [@Xie2018]. Raw data for analyses are provided in the folder 'RData' and the folder 'R' contains the R-Script that was used to export the data from the BDM database. The folder "Settings" contains a list of all the R packages (including version number) that were in the workspace when the manuscript was rendered. Note, however, that the files on the github repository might have slightly changed since submitting the manuscript. The version of all files will be archived on Zenodo upon acceptance of the manuscript.

>>>>

## Data accessibility and reproducibility of results {-}
Data and R Markdown documents (Manuscript.Rmd and Appendix_A.Rmd) to fully reproduce this manuscript including figures and tables are provided at https://github.com/TobiasRoth/NDep-Trend. An R Markdown document is written in markdown (plain text format) and contains chunks of embedded R code to produce the figures and tables [@Xie2018]. Raw data for analyses are provided in the folder 'RData' and the folder 'R' contains the R-Script that was used to export the data from the BDM database. The folder "Settings" contains a list of all the R packages (including version number) that were in the workspace when the manuscript was rendered.

The v1 release of the GitHub repository is the version  that corresponds to the initial submission  (https://github.com/TobiasRoth/NDep-Trend/releases/tag/v1), v2 is the version of the repository that corresponds to the revised version of the mansucript.The final version of the repository will be archived on Zenodo upon acceptance of the manuscript.
